Cascaded Approximation of Gaussian Blur

### 2015-05-23 cascade-blur.tex
Rename & reformat

\title{Cascaded Approximation of Gaussian Blur}
\author{Vabishchevich Nikolay}
\date{May 22, 2015}
\maketitle

@@

Third method is usually slightly better than second and much better then first, but precise methods
require good approximation of effective rescale filter $D$. Experiments shows that tight 7-tap
approximation
\begin{equation}
    D(\varphi) \approx D_0 + 2\sum_{k=1}^3 D_k\cos(k\varphi)
\end{equation}
is quite good. Coefficients here should be chosen in such a way that equation is exact up to 6
term of Taylor series around $\varphi = 0$. Corresponding problem can be solved analytically
and give the following results
\newcommand\0{\phantom{0}}
\begin{align}
    D_0 &= (   5204 +   2520\cdot4^{-n} +   1092\cdot16^{-n} +   3280\cdot64^{-n}) / 12096,\\
    D_1 &= (   2943 - \0 210\cdot4^{-n} - \0 273\cdot16^{-n} -   2460\cdot64^{-n}) / 12096,\\
    D_2 &= (\0  486 - \0 924\cdot4^{-n} - \0 546\cdot16^{-n} + \0 984\cdot64^{-n}) / 12096,\\
    D_3 &= (\0\0 17 - \0 126\cdot4^{-n} + \0 273\cdot16^{-n} - \0 164\cdot64^{-n}) / 12096.
\end{align}
Fig.~\ref{D} shows that such approximation noticeably differ from exact curve only at region near
$\varphi = \pm\pi$ where the target Gaussian is near zero anyway. Accurate approximation of
effective rescale filter kernel concludes calculation of the main filter coefficients, and in the
following section I study the task of choosing remaining parametrs $n$, $l$ and $m_i$.

>>>>

\title{Cascaded Approximation of Gaussian Blur}
\author{Vabishchevich Nikolay}
\date{May 23, 2015}
\maketitle

@@

Third method is usually slightly better than second and much better then first, but precise methods
require good approximation of effective rescale filter $D$. Experiments shows that tight 7-tap
approximation
\begin{equation}
    D(\varphi) \approx D_0 + 2\sum_{k=1}^3 D_k\cos(k\varphi)
\end{equation}
is quite good. Coefficients here should be chosen in such a way that equation is exact up to 6
term of Taylor series around $\varphi = 0$. Corresponding problem can be solved analytically
and give the following results
\newcommand\0{\phantom{0}}
\begin{align}
    D_0 &= (   5204 +   2520\cdot4^{-n} +   1092\cdot16^{-n} +   3280\cdot64^{-n}) / 12096,\\
    D_1 &= (   2943 - \0 210\cdot4^{-n} - \0 273\cdot16^{-n} -   2460\cdot64^{-n}) / 12096,\\
    D_2 &= (\0  486 - \0 924\cdot4^{-n} - \0 546\cdot16^{-n} + \0 984\cdot64^{-n}) / 12096,\\
    D_3 &= (\0\0 17 - \0 126\cdot4^{-n} + \0 273\cdot16^{-n} - \0 164\cdot64^{-n}) / 12096.
\end{align}
Fig.~\ref{D} shows that such approximation noticeably differ from exact curve only at region near
$\varphi = \pm\pi$ where the target Gaussian is near zero anyway. Accurate approximation of
effective rescale filter kernel concludes calculation of the main filter coefficients, and in the
following section I'll study the task of choosing remaining parameters $n$, $l$ and $m_i$.
